Red Wine Quality Exploration by Yiyi Tang
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

library(ggplot2)
library(dplyr)
library(knitr)
source("https://raw.githubusercontent.com/briatte/ggcorr/master/ggcorr.R")

```

```{r echo=FALSE, Load_the_Data}

wine <- read.csv('wineQualityReds.csv')

```

The dataset is about red wine quality, containing 1599 observations (wine) of \
12 variables (chemical properties of wine).The variable 'quality' (based on \
sensory data) score between 0 (very bad) and 10 (very excellent). 

# Univariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_1}

summary(wine$quality_f)
summary(wine$quality)
wine$quality_f <- factor(wine$quality, 
                       labels = c('3','4','5','6','7','8'))

```


```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_12}

str(wine)
names(wine)
summary(wine)
table(wine$quality)

```

All variables are numeric type except for quality, which is integer. I will \
create a variable named 'quality_f' as factor. 


```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_6}

qplot(x = quality, data = wine,
      binwidth=0.3,
      fill=I('grey'), 
      col=I('black'))

```

In the dataset, 'quality' variable score between 3 - 8. Above results shows \
the distribution of red wine of each quality score in the dataset. We can see \
that most red wine's quality score between 5 and 6. 



```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_2}

summary(wine$alcohol)
 qplot(x = alcohol, data = wine, 
      binwidth = 0.1)+
  scale_x_continuous(breaks = seq(8, 15, 0.5))

```

There's a peak around 9.2 - 9.8 in distribution of 'alcohol' variable. Also, I \
noticed few wine has exremely high alcohol (above 14, and between 14.5 and \
15.0) and extremely low alcohol (below 9). Let's look at these outliners in \
the alcohol.

```{r echo=FALSE, message=FALSE, warning=FALSE, by_1}

by(wine$alcohol, wine$quality, summary)

```

It looks like alcohol outliners which have extremely low alcohol (below 9) \
tend to be in low quality category 3, 4, 5 and 6, while alcohol outliners \
which have extremely high alcohol (above 14) tend to be in high quality \
category 5,6,7 and 8.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_3}

qplot(x=alcohol, data=wine)+
  facet_wrap(~quality)

qplot(x=alcohol, data=wine,
      binwidth=0.3)+
  facet_wrap(~quality)

```

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_4}

quality_group <- group_by(wine,quality)

wine.alco_by_quality <- summarise(quality_group,
                       alco_mean=mean(alcohol),
                       alco_median=median(alcohol),
                       n=n())
head(wine.alco_by_quality)

```

I grouped a subset table 'wine.alco_by_quality', describing alcohol \
categorized in quality. I noticed that the best quality category has the \
biggest mean 12.09 and median of alcohol 12.88. 

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_5}

by(wine$alcohol,wine$quality,summary)

ggplot(aes(x=quality_f, y=alcohol), data= wine)+
  geom_boxplot()+
  scale_y_continuous(breaks=seq(8,13,1),limits = c(9,13))

```

I looked at the mean and median of alcohol in each quality category, and I'm \
curious to find out if alcohol influence the quality of wine. And if there's \
other variables together with alcohol influence the quality.


```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_7}

summary(wine$citric.acid)

qplot(x = citric.acid, data = wine,
      binwidth=0.01)

```

Citric.acid is slightly skewed to the right. There's a high peak in \
'citric.acid' variable's distribution at 0.00. It's normal becasue citric.acid\
often found small quantities in wine.

There's another 3 relatively small peaks in the distribution. I also noticed \
an outliner, which is at 1.00. Because citric.acid can add 'freshness' and \
flavor to wines, I'm wondering if higher citric.acid positvely influence quality\
of wines. And if the wine which have citric.acid equal to 1 are in better \
quality.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_14}

subset(wine, citric.acid>=1)

```

While it surprised me that the wine having maximum citric.acid is in quality 4, \
which is not counted for a better quality.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_8}

summary(wine$fixed.acidity)
qplot(x = fixed.acidity, data=wine,
      binwidth=0.1,
      fill=I('grey'),
      color=I('black'))+
  scale_x_continuous(breaks=seq(4,16,1))

```


```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_9}

summary(wine$volatile.acidity)
qplot(x = volatile.acidity, data=wine,
      binwidth=0.01,
      fill=I('grey'),
      color=I('black'))+
  scale_x_continuous(breaks=seq(0,2,0.1))

```

Above two histograms show distribution of 'fixed.acidity' variable (do not \
evaporate readily) and 'volatile.acidity' variable (represent the amount of \
acetic acid in wine, which at too high of levels can lead to an unpleasant, \
vinegar taste). 


```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_10}

summary(wine$residual.sugar)
qplot(x=residual.sugar, data=wine,
      binwidth=0.1)+
  scale_x_continuous(breaks=seq(0,16,1))

```

The residual.sugar is skewed to the right, with some outliners above 11. Most \
of residual.sugar is between 1 and 3.


```{r echo=FALSE,message=FALSE, warning=FALSE, Univariate_Plots_11}

summary(wine$chlorides)
qplot(x=chlorides, data=wine,
      binwidth=0.005)+
  scale_x_continuous(breaks=seq(0,0.65,0.05))

```

Most of the chlorides are between 0.05 and 0.12. 

```{r echo=FALSE,message=FALSE, warning=FALSE, Univariate_Plots_15}

summary(wine$density)

qplot(x=density, data=wine,
      binwidth=0.0001)+
  scale_x_continuous(breaks=seq(0.99,2,0.001))

```

Around 75% wine have density 0.9978. The median density is 0.9968, and the mean\
density is 0.9967, which these two are pretty close.

```{r echo=FALSE,message=FALSE, warning=FALSE, Univariate_Plots_16}

summary(wine$pH)
qplot(x=pH, data=wine,
      binwidth=0.01)

```

pH is fairly normally distributed with a few outliners. The mean pH is 3.311, \
and around 75% of pH is 3.4. 

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_20}

quality_bucket = cut(wine$quality,3,labels=c('Low (Rating 3 - 4)','Medium (Rating 5 - 6) ','High (Rating 7 - 8)'))
table(quality_bucket)

```

```{r echo=FALSE,message=FALSE, warning=FALSE, Univariate_Plots_17}

qplot(x=quality_bucket,data=wine)

```

I created quality_bucket to group quality ratings. Wines receiving 3 and 4 quality\
score grouped in "Low" quality_bucket, wines receiving 5 and 6 quality score \
grouped in "Medium" quality_bucket, and wines receiving 7 and 8 quality score\
grouped in "High" quality_bucket.

# Univariate Analysis

### What is the structure of your dataset?
There are 1599 wine observations in the dataset with 12 features \
(fixed acidity, volatile acidity, citric acid, residual sugar, chlorides, \
free sulfur dioxide, total sulfur dioxide, density, pH, sulphates, alcohol and \
quality). The output variable quality is based on sensor data, scoring between \
0 and 10.

I set the 'quality' variable as ordered factor variable. Its levels are showed \
as below:

(very bad) -----> (very excellent)

**quality**: 0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10

While in the dataset, quality variable ranges between 3 and 8.

Other observations:

* Most wine's quality are 5 and 6.
* The mean alcohol is 10.42%, and the median alcohol is 10.20%.
* The min quality of wine in the dataset is 3, the max quality is 8, \
and the mean quality is 5.636.
* About 75% of wine contains 2.6 g / dm^3 residual.sugar. 
* The mean citric.acid is 0.271 g / dm^3, and the max citric.acid is 1 g / dm^3.

### What is/are the main feature(s) of interest in your dataset?
The main features of interest in my dataset are quality, alcohol and \
citric.acid. I'd like to know which feature or features combination are best \
for predicting the quality of wine. 

I suspect alcohol or citric.acid and some combination of the other variables\
can influence the quality of wine. This suspection may help me build a \
predictive model for wine quality in the following analysis.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?
Features like density and pH will help support my investigation \
because I suspect alcohol might influence the density of water in wine, and pH \
might be influenced by alcohol and citric.acid.

### Did you create any new variables from existing variables in the dataset?
I created 'quality_f' variable as factor for further bivariate analysis, and\
a quality bucket grouping qualities into 'low' ,'medium' and 'high'. Also\
I created a subset named 'wine.alco_by_quality' to better see if there's \
correlation between these two variables.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

* I found some outliners in alcohol variable (below 9 or above 14). Also, I 
noticed that the best quality category has the biggest mean 12.09 and median of \
alcohol 12.88. But it doesn't mean any liner or correlation between alcohol and\
quality. I will further analysize them in the following section.

* Citric.acid distribution has several peaks and is slightly skewed to the \
right. The highest peak is at 0.00, and there's another 3 relatively small \
peaks in the distribution. I also noticed an outliner, which is at 1.00. I \
checked the wine with 1.00 citric.acid and found it is in quality 4.


# Bivariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_17}

ggcorr(wine)

```

From this matrix, I noticed that among my featured interested variables (alcohol,\
quality, pH, density and citric.acid), there's some meaningful correlations I would\
like to take a look, such as correlation of quality and alcohol, alcohol and pH, \
citric.acid and density, citric.acid and pH, citric.acid and quality. Becasue \
these correlation value seem to be bigger than 0.3 or smaller than -0.3, which\
means may have a meaningful correlation.

### Relationship between alcohol and quality 

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_1}

ggplot(aes(x=alcohol,y=quality),data=wine)+
  geom_jitter(alpha=0.3,color='orange')+
  geom_smooth(method=lm,se=FALSE,size=1)+
  scale_x_continuous(breaks=seq(9,14,1))+
  xlim(9,14)

```

I removed outliners in alcohol to see if the relationship between alcohol and \
quality would be stronger. It turned out just a little bit stronger. So It's \
better to use Pearson's correlation to test these two. And maybe there's more \
variables participate into this relationship. 

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_2}
ggplot(aes(x=quality_f, y=alcohol,color=quality_f), data= wine)+
  geom_boxplot()+
  geom_jitter(alpha=0.3,size=1)+
  scale_color_brewer(type="seq",
                     guide=guide_legend(title='Quality Groups'))

```

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_3}

cor.test(wine$alcohol, wine$quality)

```

Above Pearson's correlation result shows there's a moderate correlation between \
alcohol and quality. To be more specific, wine with higher alcohol tend to be \
in better quality.
### Relationship between citric.acid and density

```{r}

ggplot(aes(x=citric.acid,y=density),data=wine)+
  geom_point(alpha=0.3,size=1)+
  geom_smooth(method=lm, se=FALSE, size=0.6)

```

```{r}
cor.test(wine$citric.acid,wine$density)
```

There's a positive meaningful but small correlation between citric.acid and density.

### Relationship between alcohol and pH

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_5}

ggplot(aes(x=pH,y=alcohol),data=wine)+
  geom_point(alpha=0.3)+
  coord_trans(x='sqrt')+
  geom_smooth(method=lm,se=FALSE,size=1)

cor.test(wine$alcohol,wine$pH)
```

Alcohol and pH have few correlation.

### Relationship between alcohol and density

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_6}

ggplot(aes(x=alcohol,y=density),data=wine)+
  geom_point(alpha=0.3, color='orange')+
  coord_trans(y='sqrt')+
  geom_smooth(method=lm,se=FALSE,size=1)

cor.test(wine$alcohol,wine$density)

```

There's a moderate correlation between alcohol and density variables. To be \
specific, wine with higher alcohol tend to have lower density. 

### Relationship between citric.acid and quality

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_8}

ggplot(aes(x=citric.acid,y=quality),data=wine)+
  geom_jitter(alpha=0.3,color='orange')+
  geom_smooth(method=lm,se=FALSE,size=1)

cor.test(wine$citric.acid,wine$quality)

```

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_9}

ggplot(aes(x=quality_f,y=citric.acid),data=wine)+
  geom_boxplot()+
  ylim(0,0.6)

```

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_10}

by(wine$citric.acid,wine$quality,summary)

```

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_19}
by(wine$citric.acid,wine$quality,summary)

wine.citric_by_quality <- summarise(quality_group,
                                    citric_mean=mean(citric.acid),
                                    n())
head(wine.citric_by_quality)

ggplot(aes(x=quality,y=citric_mean), data=wine.citric_by_quality)+
  geom_jitter(color='blue')+
  geom_smooth(method=lm, color='grey')

```

Better quality wine have bigger mean of citric.acid.


While citric.acid would add 'freshness' or flavor to wine, there's few correlation\
between quality and citric.acid. But there's a tendency that better quality wine\
has higher mean citric.acid. 

### Relationship between citric.acid and alcohol

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_11}

ggplot(aes(x=citric.acid,y=alcohol),data=subset(wine,citric.acid>0))+
  geom_jitter(alpha=0.3,color='orange')+
  scale_y_log10()+
  geom_smooth(method=lm,se=FALSE,size=1)

cor.test(wine$citric.acid,wine$alcohol)

```

Few correlation between citric.acid and alcohol.

### Relationship between pH and density

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_12}

ggplot(aes(x=density, y=pH),data=wine)+
  geom_point(alpha=0.3,color='orange')+
  geom_smooth(method=lm,se=FALSE,size=1)

```


```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_13}

cor.test(wine$pH, wine$density)

```

There's a meaningful but small correlation between pH and density. 

### Relationship between pH and citric.acid

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_14}

ggplot(aes(x=citric.acid,y=pH),data=wine)+
  geom_point(color='orange',alpha=0.3)+
  geom_smooth(method=lm,se=FALSE,size=1)

```

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_15}

cor.test(wine$citric.acid,wine$pH)

```

pH and citric.acid have a moderate negative correlation around -0.5419.

# Bivariate Analysis

> **Tip**: As before, summarize what you found in your bivariate explorations
here. Use the questions below to guide your discussion.

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

* From the ggcorr correlation matrix, I found there might be some meaningful \
correlation between quality and alcohol, alcohol and pH, citric.acid and density,\
citric.acid and pH, citric.acid and quality.

* I found alcohol and quality have a moderate correlation that wine with \
higher alcohol tend to be in better quality.The correaltion is around 0.476.

* Few correlation is existed between quality and citric.acid. But I found that \
better quality wine has higher mean citric.acid. For example, the mean citric.acid\
of quality 8 wine is 0.3911, while the mean citric.acid of quality 4 wine is 0.1742.

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

* There???s a moderate correlation between alcohol and density. To be
specific, wine with higher alcohol tend to have lower density. The correlation \
is around -0.496.

*citric.acid and density have a meaningful but small correlation around 0.36.

* pH and density have a meaningful but small correlation around -0.34. To be \
specific, when density increase, pH tend to decrease.

* pH and citric.acid have a moderate negative correlation around -0.5419.

### What was the strongest relationship you found?

pH and citric.acid have the strongest relationship in my finding.

# Multivariate Plots Section

### Alcohol and density in quality category
```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_1}

ggplot(aes(x=alcohol, y=density, color=quality_f), 
       data = wine) +
      geom_point(alpha=0.2, size=1) +
      geom_smooth(method ="lm", se=FALSE,size=0.6)  +
  scale_color_brewer(type='seq',
                   guide=guide_legend(title='Quality'))

```

It's hard to see the results because of so much different colors. So I created \
quality_bucket for better visualization.

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_3}

ggplot(aes(x=alcohol,y=density,color=quality_bucket),data=wine)+
  geom_point(alpha=0.2,size=1)+
  geom_smooth(linetype=1,method=lm,size=0.6)+
  scale_color_brewer(type="seq",
                     guide=guide_legend(title='Quality Groups'))

```

It seems like three quality groups follow the relationship between density and \
alcohol. 

### Density and pH in quality category
```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_4}

ggplot(aes(x=density, y=pH,color=quality_bucket),data=wine)+
  geom_point(alpha=0.2,size=1)+
  geom_smooth(method=lm,se=FALSE,size=0.6)+
  scale_color_brewer(type="seq",
                     guide=guide_legend(title = 'Quality Groups'))

```

Quality groups follow the relationship of pH and density. And it's clear to see\
that low quality group has shorter range of pH and density, compared with medium\
and high quality group.

### Citric.acid and pH in quality category

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_5}

ggplot(aes(x=citric.acid,y=pH,color=quality_bucket),data=wine)+
  geom_point(alpha=0.3,size=1)+
  geom_smooth(method=lm, se=FALSE, size=0.6)+
  scale_color_brewer(type="seq",
                     guide=guide_legend(title='Quality Groups'))

```

Quality groups follow the relationship of pH and citric.acid. The low quality\
group has a relatively bigger range of citric.acid. Also, I noticed there's a lot\
medium quality wine have 0 citric.acid, compared to low and high quality groups. 

### Citric.acid and density in quality category

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_6}

ggplot(aes(x=citric.acid,y=density,color=quality_bucket),data=wine)+
  geom_point(alpha=0.3,size=1)+
  geom_smooth(method=lm, se=FALSE, size=0.6)+
  scale_color_brewer(type="seq",
                     guide=guide_legend(title='Quality Groups'))

```

### Calculate r-squared value 

By calculating r-squared value, I want to test if the strongest variable alcohol\
would strong r-squared value to proof its linear relationship with quality. 

```{r message=FALSE, warning=FALSE, Multivariate_Plots_7}
m1 <- lm(wine$quality ~ wine$alcohol)
m2 <- lm(wine$quality ~ wine$alcohol+wine$density)
m3 <- lm(wine$quality ~ wine$alcohol+wine$density+wine$citric.acid)
m4 <- lm(wine$quality ~ wine$alcohol+wine$density+wine$citric.acid+wine$pH)

summary(m1)$r.squared
summary(m2)$r.squared
summary(m3)$r.squared
summary(m4)$r.squared
```

I chose alcohol (have the strongest correlation with quality among my interested\
variable) to test the lineary relation with quality. Unfortunately, the r-squared \
is not strong (0.22673).

But when I added each of the variables of interest into this model, the r-squared\
value did improve from 0.22673 to 0.2626.

```{r message=FALSE, warning=FALSE, Multivariate_Plots_8}
m5 <- lm(wine$density ~ wine$alcohol)
summary(m5)$r.squared
```

Weak r-squared value to proof linear correlation between alcohol and density.

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

* From bivariate analysis I found out that density and alcohol have a modereate \
negative correlation. And from multivarite analysis by adding quality groups into \
the plot, I found out that quality gourps follow the relationship of density and\
alcohol.

* I noticed that among my featured variables, alcohol has the strongest \
relationship with quality. So I calculated its r-squared value. Although the \
r-squared value between them is not strong (around 0.22673), it did improve \
from 0.22673 to 0.22626 when I added variables, such as \
density, citric.acid and pH, into the model.

### Were there any interesting or surprising interactions between features?

* Depending on the Pearson correlation value, I thought the r-squared value \
between alcohol and quality must be strong, at least bigger than 0.5. But it \
turned out my suspection was wrong. But it did surprised my that the r-squared \
value increased every time I added another featured variables into the model. 

* It also surprised me that quality groups all follow the meaningful relationships \
which I found in bivariate analysis. To be specific, quality groups follow the \
relationships of alcohol and density, density and pH, pH and citric.acid.

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

I created a math linear model.I sed quality as dependent variable, and alcohol as\
independent variable. After I found out the r-squared value is not strong enough,\
I added citric.acid, density, and pH one at a time as independent variable into \
the model. The result r-squared value did improve, but still not strong enough.

The model clearly shows each r-squared value when you added a new featrued variable.\
So it's easy and clear to see the result that if they have linear correlation. \
But there's limitations of this model. Since I didn't put all the variables in the\
dataset to test the model. There may still be some major variable that I didn't\
include in the model.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
ggplot(aes(x=alcohol,y=density,color=quality_bucket),data=wine)+
  geom_point(alpha=0.2,size=1)+
  geom_smooth(linetype=1,method=lm,size=0.6,se=FALSE)+
  scale_color_brewer(type="seq",
                     guide=guide_legend(title='Quality Groups'))+
  labs(x="Alcohol (% by volume)",
       y="Density (g / cm^3)",
       title="Density and Alcohol in Quality Groups")
```

### Description One
Alcohol and density have a moderate negative correlation around -0.496. Wine with\
higher alcohol percentage by volume tend to have lower density (g / cm^3). And\
all wine quality groups follow the relationship of alcohol and density.

### Plot Two
```{r echo=FALSE, Plot_Two}
ggplot(aes(x=quality_f, y=alcohol,color=quality_f), data= wine)+
  geom_boxplot()+
  geom_jitter(alpha=0.3,size=1)+
  scale_color_brewer(type="seq",
                     guide=guide_legend(title='Quality Groups'))+
  labs(x="Quality",
       y="Alcohol (% by volume)",
       title="Alcohol and Quality")

```

### Description Two
Alcohol have strongest correlation with quality around 0.476. Wines with higher \
alcohol percentage by volume tend to be in better quality.But I did notice that \
wine with quality scoring 5 is a bit out of the line. It might because there's \
still potential variables (toghether with alcohol to influence quality) that I \
didn't discuss.

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(aes(x=citric.acid,y=pH,color=quality_bucket),data=wine)+
  geom_point(alpha=0.3,size=1)+
  geom_smooth(method=lm, se=FALSE, size=0.6)+
  scale_color_brewer(type="seq",
                     guide=guide_legend(title='Quality Groups'))+
  labs(x="Citric acid (g / dm^3)",
       y="pH",
       title="pH and Citric Acid")
```

### Description Three
pH and citric acid (g / dm^3) have a moderate negative correlation around -0.5419.\
Wine with higher citric acid (g / dm^3 ) tend to have lower pH. And all wine quality\
groups follow this relationship of pH and citric acid. Also, low quality group of\
wine tend to have larger range of citric acid (g / dm^3), compared to medium and \
high quality group of wines.


# Reflection

This Red Wine Quality dataset contained 1,599 observations of red wines. There're\
12 variables in the dataset, including 11 variables of chemical properties in \
these wines, and 1 output variable of wine quality, which graded by experts and \
is between 0 (very bad) and 10 (very excellent).

I'm interested in exploring how these chemical properties influence the quality \
of wine. Through univariate, bivariate, multivariate analysis and statistical \
analysis, I tested different relationships between these variables. 

Among the variables included in the dataset, alcohol had the strongest correlation\
with wine quality. The correlation is around 0.476. Wines with higher alcohol \
percentage by volume tend to be in better quality. Unfortunately, the calculated\
r-squared value between alcohol and quality is not strong (around 0.22673). But \
when I added each of the variables (which I'm interested in this dataset) one at \
a time into this model, the r-squared value did improve from 0.22673 to 0.2626.

I think the limitations of this dataset would be one of the major challenges. \
Amond 1,599 obeservations of wines, 82.4% of wines received score of 5 or 6. \
Around 4% of wines received score of 3 or 4, and 13.6% of wines received score \
of 7 or 8. It would be better to have a larger variety of quality score for the \
dataset.

For future further analysis, it would be interesting and meanfing to combine or\
compare this dataset with the white wine datast. So we can see how these chemical\
properties' correlation with quality changed.

# Reference:
* P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis.\ 
Modeling wine preferences by data mining from physicochemical properties.\
In Decision Support Systems, Elsevier, 47(4):547-553. ISSN: 0167-9236.
* https://www.linkedin.com/pulse/regression-analysis-how-do-i-interpret-r-squared-assess-gaurhari-dass
* https://discussions.udacity.com/t/how-to-quantify-correlation-between-categorical-and-numerical-variable/47067
* https://stackoverflow.com/questions/21945156/ggplot-geom-boxplot-and-geom-jitter
* https://briatte.github.io/ggcorr/#controlling-the-coefficient-labels

